The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-06-06 exp-resurgence.tex
Fix the convolution prodcut

\begin{draft}Then, the Borel regularity of thimble integrals is established by the following theorem:\end{draft}

@@

Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point. Let $\zeta_\alpha$ be the translation chart with $\zeta = \alpha + \zeta_\alpha$. The Laplace transforms $\laplace_{\zeta_\alpha, 0}$ and $\laplace_{\zeta, \alpha}$, which both turn functions on $B$ into functions on $T^*_{\zeta = \alpha}B$, are related in the following way.

@@

@@

@@

@@

\begin{todo}[Correct and rewrite!]\end{todo}
\begin{old}The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.\end{old}
\begin{todo}[Check: if Laplace transform of convolution is well-defined, then product of Laplace transforms is well-defined]\end{todo}
\begin{todo}[\textbf{A} \textbf{V} Redo argument with $\ast_{\zeta, \beta}$]\end{todo}
\laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] & = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,0}[{\psi}]

@@

   \textbf{V} fix notation, add $\theta$

@@

   First we notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
       \phi \ast_{\zeta, \alpha} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta''\\
   where $\zeta'=s\zeta_\alpha+\alpha$ and consequently $\zeta''=\zeta_\alpha (1-s)$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
       \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta, \alpha}{\psi}]&=e^{-z\alpha}\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta, \alpha}{\psi}]\\
       &=e^{-z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi' \psi''\,ds \\
       &=e^{-z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi' \psi''\,ds 

@@

        &=\int_0^1 ds\,\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z(\zeta_\alpha s+\alpha)} \phi' \psi'' \\
        &=\int_0^1 ds\,\int_{\Gamma_{\zeta'',0}}d\zeta''\,\frac{\zeta''}{(1-s)^2}\,e^{-z\zeta''} e^{-z(\zeta'' \frac{s}{1-s}+\alpha)} \phi' \psi'' 
   Exchanging one more time the order of integration we get
        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_0^1 ds\,\frac{\zeta''}{(1-s)^2}e^{-z(\zeta'' \frac{s}{1-s}+\alpha)} \phi'\\
        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\Gamma_{t,\alpha}} dt\, e^{-zt} \phi\\
   where we have introduced the coordinate $t=\zeta''\frac{s}{1-s}+\alpha$ which gives the ray $\Gamma_{t,\alpha}$ as $s$ varies in $[0,1]$. \begin{todo}[Check claim: as coordinates on the position domain, $t = \zeta'$. If true, clarify argument.]\end{todo}

>>>>

\begin{revised}Once we know $\iota_a$, we can go through the steps of the Borel regularization process and show that we end up with the same function we started with.\end{revised}

@@

\begin{todo}[Change $b$ to $\alpha$?]\end{todo} Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point. Let $\zeta_\alpha$ be the translation chart with $\zeta = \alpha + \zeta_\alpha$. The Laplace transforms $\laplace_{\zeta_\alpha, 0}$ and $\laplace_{\zeta, \alpha}$, which both turn functions on $B$ into functions on $T^*_{\zeta = \alpha}B$, are related in the following way.

@@

    \begin{definition}%\label{def:convolution}

@@

\begin{equation}%\label{eq:convolution_def}

@@

% \begin{todo}[Correct and rewrite!]\end{todo}
% \begin{old}The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.\end{old}
% \begin{todo}[Check: if Laplace transform of convolution is well-defined, then product of Laplace transforms is well-defined]\end{todo}
% \begin{todo}[\textbf{A} Redo argument with $\ast_{\zeta, \beta}$]\end{todo}
% \begin{draft}
% \begin{align*}
% \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] & = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,0}[{\psi}]
% \end{align*}
% \end{draft}
Let $\phi,\psi$ be two holomorphic functions on $B$. Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta=\alpha$, then the convolution product $\phi\ast_{\zeta,\alpha}\psi$ is an holomorphic function on $B$ defined as
\phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta)\times\mathcal{S}''(\zeta)\\ \zeta'+\zeta''=\zeta}} \phi' \psi'' d\zeta'
where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$, and $\mathcal{S}''(\zeta)$ is defined similalrly. \begin{todo}
    Is it clear the convolution is holomorphic??
On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$. The Laplace transform $\laplace_{\zeta_\alpha, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta_\alpha, 0}$.
\begin{prop}\label{prop:convolution_iso_laplace}
Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined. Then 
    \laplace_{\zeta_\alpha,0}[\phi\ast_{\zeta_\alpha,0}\psi]=\laplace_{\zeta_\alpha,0}[\phi]\,\laplace_{\zeta_\alpha,0}[\psi]\,.
Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
       \phi \ast_{\zeta, \alpha} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'\\
where $\zeta'=s\zeta_\alpha$ and consequently $\zeta''=\zeta_\alpha (1-s)$.

First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$. Indeed it is uniform of exponential type
   \big|\phi \ast_{\zeta_\alpha,0} \psi\big|&\leq |\zeta_\alpha|\int_0^1 ds \,|\phi'|\,|\psi''|\\
   &\lesssim |\zeta_\alpha| \int_0^1 ds\, e^{c |\alpha+s\zeta_\alpha|}\,e^{c'|(1-s)\zeta_\alpha|}\\
   & \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}
where $c''=\max\{c,c'\}$. \begin{todo}
    How do we check it is locally integrable???
Then, the Laplace transform of $\phi \ast_{\zeta_\alpha,0} \psi$ reads
       \laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]&=\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]\\
       &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi' \psi''\,ds \\
       &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z s \zeta_\alpha} \phi' \psi''\,ds 
        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi' \psi'' \\
        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta'',0}}d\zeta''\,\frac{\zeta''}{(1-s)^2}\,e^{-z\zeta''} e^{-z\zeta'' \frac{s}{1-s}} \phi' \psi'' 
   Setting $t=\zeta''\frac{s}{1-s}$ we find
        &=\int_{\mathcal{J}_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi''\,\int_0^1 ds\,\frac{\zeta''}{(1-s)^2}e^{-z\zeta'' \frac{s}{1-s}} \phi'\\
        &=\int_{\mathcal{J}_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\mathcal{J}_{t,0}} dt\, e^{-zt} \phi\\
   where as $s$ varies in $[0,1]$ we get that $t$ follows the ray $\mathcal{J}_{t,0}$. 
More generally we can show that the product of two Laplace transforms based at different points is the Laplce transform of the convolution.

@@

Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transforms $\laplace_{\zeta,\alpha}\phi$ and $\laplace_{\zeta,\beta}\psi$ are well defined. Then 
    \laplace_{\zeta,\alpha+\beta}[\phi\ast_{\zeta,\alpha+\beta}\psi]=\laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.

@@

   \textbf{V} add $\theta$

@@

  Notice that the convolution product can be rewritten by introducing the coordinates $\eta'=\zeta'-\beta$ and $\eta''=\zeta''+\beta$
       \phi \ast_{\zeta, \alpha+\beta} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'\\
       &=\int_{\substack{\mathcal{S}'(\eta) \times \mathcal{S}''(\eta) \\ \eta' + \eta'' = \zeta}} \phi'\,\psi''\,d\eta'\,,
   where $\mathcal{S}'(\eta)$ is the line segment from $\eta'=\alpha$ to $\eta'=\zeta_\beta$ and simlarly, $\mathcal{S}''(\eta)$ is the line segment from $\eta''=\zeta_\alpha$ to $\eta''=\beta$. \begin{todo}\textbf{V} [explain why this choice of coords is better than $\eta'$ and $\eta''$]\end{todo} Following the argument in the proof of Proposition~\ref{prop:convolution_iso_laplace}, we introduce the parameter $s\in [0,1]$ and we rewrite the convolution  
       \phi \ast_{\zeta, \alpha+\beta} \psi
       &=\int_{\substack{\mathcal{S}'(\eta) \times \mathcal{S}''(\eta) \\ \eta' + \eta'' = \zeta}} \phi'\,\psi''\,d\eta'\\
       &=\zeta_{\alpha+\beta}\,\int_0^1 \phi' \psi''\,ds\,,
   where $\eta'=(1-s)\alpha+s\zeta_\beta$ and consequently $\eta''=\beta s+(1-s)\zeta_\alpha$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
       \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=e^{-z(\alpha+\beta)}\laplace_{\zeta_{\alpha+\beta},0}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]\\
       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi' \psi''\,ds \\
       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\, \int_0^1 \zeta_{\alpha+\beta}\,e^{-z(1-s)\zeta_{\alpha+\beta}} e^{-z s\zeta_{\alpha+\beta}} \phi' \psi''\,ds 

@@

        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,\zeta_{\alpha+\beta}\,e^{-z(\alpha(1-s)+s\zeta_\beta)} e^{-z(\beta s+(1-s)\zeta_\alpha)} \phi' \psi'' \\
        &=\int_0^1 ds\,\int_{\mathcal{J}_{\eta'',\beta}}d\eta''\,\frac{\eta''}{(1-s)^2}\,e^{-z\eta''} (\eta''-\beta) e^{-z( (\eta''-\beta) \frac{s}{1-s}+\alpha)} \phi' \psi''\,,
   where in the second step we use $d\zeta_{\alpha+\beta}=d\zeta_\alpha=\frac{d\eta''}{1-s}$ and $\zeta_{\alpha+\beta}=\frac{\eta''-\beta}{1-s}$. Then, exchanging one more time the order of integration we get
        &=\int_{\mathcal{J}_{\eta'',0}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_0^1 ds\,\frac{\eta''-\beta}{(1-s)^2}e^{-z((\eta''-\beta) \frac{s}{1-s}+\alpha)} \phi'\\
        &=\int_{\mathcal{J}_{\eta'',0}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_{\mathcal{J}_{t,\alpha}} dt\, e^{-zt} \phi\\
   where we have introduced the coordinate $t=(\eta''-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{t,\alpha}$ as $s$ varies in $[0,1]$. \begin{todo}[Check claim: as coordinates on the position domain, $t = \eta'$. If true, clarify argument.]\end{todo}
